\LARGE \bf Reactive Trajectory Planning and Tracking for Pedestrian-Aware Autonomous Driving in Urban Environments

### 2016-04-14 root.tex
fixed question mark places

For human passengers, it is widely believed that high levels of jerk (time derivative of acceleration) and high acceleration and velocity values are prime contributors to ride discomfort.
Lot of work has been performed on optimizing these constraints for highways and country roads ~\cite{ziegler14,bahram15,xu12,CHEB15CI}.
Similar work performed by Bianco et al \cite{GuarinoLoBianco2004,GuarinoLoBianco2005,Bianco2007,Bianco2009,GuarinoLoBianco2013} sets the travel time a priori and optimally minimizes ???what????? without hard limitations or direct jerk control.
Other work on optimizing these constraints on urban roads ~\cite{Rastelli14,Li15} doesn't consider reactive behaviors such as responding to pedestrians and other dynamic objects in the scene.

@@

\begin{figure}
  \begin{algorithmic}[1]
    \Procedure{SegmentBoundarySpeeds}{$v_m$}
      \State $\mathbf{v}_p \gets \mathbf{v}_m$ \Comment{Initialize targets as ceilings}
      \State $\mathbf{v}_{p,0} \gets v_i$ \Comment{Set starting speed to current}
      \State $\mathbf{v}_p = [\mathbf{v}_p, 0]$ \Comment{Add final speed of 0}
      \For{$i = 1, ..., N-1$}
        \If{$v_{m,i+1} > v_{m,i}$}
          \State $v_{p,i+1} \gets v_{m,i+1}$
        \Else
          \State $v_{p,i+1} \gets v_{m,i}$
        \EndIf
      \EndFor
    \EndProcedure
  \end{algorithmic}
  \caption{
    Algorithm to set speed boundary conditions for interior segments.
    Having consolidated the waypoints into a set of path segments, the maximum allowable speed for each segment, $v_{m,i}$ is known.
    This algorithm uses the set of $\mathbf{v_{m}}$ for all segments to choose the highest allowable start and end speeds for each path segment.
    ????????? define $v_p$ ???????????
  }
\label{alg:segmentspeedboundaryconditions}
\end{figure}

>>>>

For human passengers, it is widely believed that high levels of jerk (time derivative of acceleration) and high acceleration and velocity values are prime contributors to ride discomfort.
Lot of work has been performed on optimizing these constraints for highways and country roads ~\cite{ziegler14,bahram15,xu12,CHEB15CI}.
Similar work performed by Bianco et al \cite{GuarinoLoBianco2004,GuarinoLoBianco2005,Bianco2007,Bianco2009,GuarinoLoBianco2013} sets the travel time a priori and optimally minimizes jerk without hard limitations or direct jerk control.
Other work on optimizing these constraints on urban roads ~\cite{Rastelli14,Li15} doesn't consider reactive behaviors such as responding to pedestrians and other dynamic objects in the scene.

@@

\begin{figure}
  \begin{algorithmic}[1]
    \Procedure{SegmentBoundarySpeeds}{$v_m$}
      \State $\mathbf{v}_p \gets \mathbf{v}_m$ \Comment{Initialize targets as ceilings}
      \State $\mathbf{v}_{p,0} \gets v_i$ \Comment{Set starting speed to current}
      \State $\mathbf{v}_p = [\mathbf{v}_p, 0]$ \Comment{Add final speed of 0}
      \For{$i = 1, ..., N-1$}
        \If{$v_{m,i+1} > v_{m,i}$}
          \State $v_{p,i+1} \gets v_{m,i+1}$
        \Else
          \State $v_{p,i+1} \gets v_{m,i}$
        \EndIf
      \EndFor
    \EndProcedure
  \end{algorithmic}
  \caption{
    Algorithm to set speed boundary conditions for interior segments.
    Having consolidated the waypoints into a set of path segments, the maximum allowable speed for each segment, $v_{m,i}$ is known.
    This algorithm uses the set of $\mathbf{v_{m}}$ for all segments to choose the highest allowable start and end speeds for each path segment.
  }
\label{alg:segmentspeedboundaryconditions}
\end{figure}
